### 2020-04-18 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.Rmd
Updated the analysis to include hours of sunshine, revised the abstract and introduction to reflect this change, recreated the README.md document

---
title: A spatial analysis of the environmental correlates of COVID-19 incidence in Spain
author:
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
  - name: Fernando A. Lopez
    email: fernando.lopez@upct.es
    affiliation: Universidad Politecnica de Cartagena
  - name: Tatiane Menezes
    email: tatiane.menezes@ufpe.br
    affiliation: Departamento de Economia
  - name: Renata Cavalcanti
    email: renata.vcsantos@gmail.com
    affiliation: Nucleo de Pesquisa
  - name: Maira Galdino da Rocha Pitta
    email: mgrpitta@ufpe.br
    affiliation: Nucleo de Pesquisa
address:
  - code: McMaster University
    address: School of Geography and Earth Sciences, McMaster University, 1281 Main St W, Hamilton, ON, L8S 4K1, Canada
  - code: Universidad Politecnica de Cartagena
    address: Departamento de Metodos Cuantitativos, Ciencias Juridicas, y Lenguas Modernas, Universidad Politecnica de Cartagena, Calle Real Numero 3, 30201, Cartagena, Murcia, Spain
  - code: Departamento de Economia
    address: Departamento de Economia, Universidade Federal de Pernambuco, Av dos Economistas, s/n - Cidade Universitária, Recife - PE, 50670-901, Brasil  
  - code: Nucleo de Pesquisa
    address: Núcleo de Pesquisa em Inovação Terapêutica NUPIT / UFPE, Av. Prof. Moraes Rego, 1235 - Cidade Universitária, Recife, PE, CEP 50670-901, Brazil  
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  Spreading with astonishing speed, the novel SARS-CoV2 has swept the globe, causing enormous stress to health systems and prompting social distance guidelines and mandates to arrest its progress. While there is encouraging evidence that early public health interventions have slowed the spread of the virus, this has come at a high cost as the global economy is brought to its knees. How and when to ease restrictions to movement hinges in part on the question whether SARS-CoV2 will display seasonality associated with variations in temperature and humidity. In this research, we address this question by means of a spatial analysis of the incidence of COVID-19 in the provinces in Spain. Use of a spatial Seemingly Unrelated Regressions (SUR) approach allows us to model the incidence of reported cases of the disease per 100,000 population, as a function of temperature and humidity, while controlling for GDP per capita, population density, percentage of older adults in the population, and presence of mass transit systems. An interesting aspect of the spatial SUR approach is that it models incidence as a contagion process. Our results indicate that incidence of the disease is lower at higher temperatures. The evidence with respect to humidity is more mixed, with coefficients for this variable that are significant in only some equations. Our control variables also yield interesting insights, as population density and percentage of older adults display negative associations with incidence of COVID-19, whereas the presence of mass transit systems in the province is associated with a greater incidence of the disease.    
journal: "Geographical Analysis"
date: "`r Sys.Date()`"
bibliography: References.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

Some of what is thought about the possible seasonality of COVID-19 is based on analogies to the patterns of other known respiratory viruses. However, de Ángel Solá et al. [-@deangel2020weathering] note that "not all seasonal respiratory viruses experience the same spatiotemporal patterns" (section 4). This urges caution when extrapolating from known viruses, and indeed, the evidence in this respect is inconclusive. At a global scale, whereas de Ángel Solá et al. [-@deangel2020weathering] see less risk in the Caribean Basin, Coelho et al. [@Coelho2020exponential] warn that at least during the exponential phase, expansion of the virus is not driven by climate. Similarly, whereas Araujo and Naimi [-@Araujo2020spread] argue that spread of SARS-CoV2 will likely be constrained by climate, Harbert et al. [-@Harbert2020spatial] remain unconvinced that spatial modelling can currently discriminate the distribution of the disease on the basis of climate, at least in the United States. To further complicate matters, much of the relevant work has yet to be peer-reviewed and therefore is open to change (see for example the challenge of @Harbert2020spatial to @Araujo2020spread). In the United States, the National Academy of Sciences, Engineering, and Medicine was engaged by the Office of the Executive for guidance on this matter [see @National2020rapid]. Their conclusion summarizes the situation well (see p. 6): "Some limited data support a potential waning of cases in warmer and more humid seasons, yet none are without major limitations...Additional studies as the SARS-CoV-2 pandemic unfolds could shed more light on the effects of climate on transmission."

With the above considerations in mind, our objective with this paper is to contribute to the knowledge basis regarding the spread of COVID-19 and the influence of environmental factors, particularly temperature and humidity. Hence, here we report results from a spatial analysis of incidence of COVID-19 in fifty provinces in Spain. Spain is one of the countries hardest hit by the virus, and enacted lockdown measures on March 16, 2020, in response to a rapidly growing outbreak of COVID-19. We combine data on reported cases of the disease with metereological information, to create a spatio-temporal dataset covering a period of 30 days. We then join this dataset with provincial-level economic and demographic information to act as controls to our key environmental variables. These data are analyzed using a spatial Seemingly Unrelated Regressions (SUR) approach, which allows us to model incidence of COVID-19 as a spatial contagion process.

The results provide evidence of the effect of temperature on the incidence of COVID-19. The evidence concerning humidity is more mixed: while the direction of the effect is negative, as anticipated, the coefficients for this variable are only significant in some of equations in the system. Our control variables also provide some intriguing insights. The results of this analysis provide support to the hypothesis of seasonality of the novel SARS-CoV2, and should be of interest to public health officials and policy makers wrestling with the question of the trajectory of the pandemic.

>>>>

---
title: A spatial analysis of the environmental correlates of COVID-19 incidence in Spain
author:
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
  - name: Fernando A. Lopez
    email: fernando.lopez@upct.es
    affiliation: Universidad Politecnica de Cartagena
  - name: Tatiane Menezes
    email: tatiane.menezes@ufpe.br
    affiliation: Departamento de Economia
  - name: Renata Cavalcanti
    email: renata.vcsantos@gmail.com
    affiliation: Nucleo de Pesquisa
  - name: Maira Galdino da Rocha Pitta
    email: mgrpitta@ufpe.br
    affiliation: Nucleo de Pesquisa
address:
  - code: McMaster University
    address: School of Geography and Earth Sciences, McMaster University, 1281 Main St W, Hamilton, ON, L8S 4K1, Canada
  - code: Universidad Politecnica de Cartagena
    address: Departamento de Metodos Cuantitativos, Ciencias Juridicas, y Lenguas Modernas, Universidad Politecnica de Cartagena, Calle Real Numero 3, 30201, Cartagena, Murcia, Spain
  - code: Departamento de Economia
    address: Departamento de Economia, Universidade Federal de Pernambuco, Av dos Economistas, s/n - Cidade Universitária, Recife - PE, 50670-901, Brasil  
  - code: Nucleo de Pesquisa
    address: Núcleo de Pesquisa em Inovação Terapêutica NUPIT / UFPE, Av. Prof. Moraes Rego, 1235 - Cidade Universitária, Recife, PE, CEP 50670-901, Brazil  
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  Spreading with astonishing speed, the novel SARS-CoV2 has swept the globe, causing enormous stress to health systems and prompting social distance guidelines and mandates to arrest its progress. While there is encouraging evidence that early public health interventions have slowed the spread of the virus, this has come at a high cost as the global economy is brought to its knees. How and when to ease restrictions to movement hinges in part on the question whether SARS-CoV2 will display seasonality associated with variations in temperature, humidity, and hours of sunshine. In this research, we address this question by means of a spatial analysis of the incidence of COVID-19 in the provinces in Spain. Use of a spatial Seemingly Unrelated Regressions (SUR) approach allows us to model the incidence of reported cases of the disease per 100,000 population, as a function of temperature and humidity, while controlling for GDP per capita, population density, percentage of older adults in the population, and presence of mass transit systems. An interesting aspect of the spatial SUR approach is that it models incidence as a contagion process. Our results indicate that incidence of the disease is lower at higher temperatures and higher levels of humidity, although coefficients for this variable are significant only in some equations. Sunshine, in contrast, displays a positive association with incidence of the disease. Our control variables also yield interesting insights. Higher incidence is associated with higher GDP per capita and presence of mass transit systems in the province; in contrast, population density and percentage of older adults display negative associations with incidence of COVID-19.    
journal: "Geographical Analysis"
date: "`r Sys.Date()`"
bibliography: References.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

Some of what is thought about the possible seasonality of COVID-19 is based on analogies to the patterns of other known respiratory viruses. However, de Ángel Solá et al. [-@deangel2020weathering] note that "not all seasonal respiratory viruses experience the same spatiotemporal patterns" (section 4). This urges caution when extrapolating from known viruses, and indeed, the evidence in this respect is inconclusive. At a global scale, de Ángel Solá et al. [-@deangel2020weathering] see less risk in the Caribean Basin; however, Coelho et al. [@Coelho2020exponential] warn that at least during the exponential phase, expansion of the virus is not driven by climate. Similarly, whereas Araujo and Naimi [-@Araujo2020spread] argue that spread of SARS-CoV2 will likely be constrained by climate, Harbert et al. [-@Harbert2020spatial] remain unconvinced that spatial modelling can currently discriminate the distribution of the disease on the basis of climate, at least in the United States. Yao et al. [-@Yao2020association], examined data from China and came to the conclusion that neither temperature nor ultraviolet indices had an association with transmission of COVID-19. This is despite previous research that has linked less exposure to UVB radiation to higher prevalence and severity of acute respiratory tract infections (Zittermann et al. 2016; Dąbrowska-Leonik et al. 2018; Dinlen et al. 2016; Mathyssen et al. 2017; Esposito and Lelii 2015; Jat 2017; Moriyama, Hugentobler, and Iwasaki 2020). To further complicate matters, much of the relevant work has yet to be peer-reviewed and therefore is open to change (see for example the challenge of @Harbert2020spatial to @Araujo2020spread). In the United States, the National Academy of Sciences, Engineering, and Medicine was engaged by the Office of the Executive for guidance on this matter [see @National2020rapid]. Their conclusion summarizes the situation well (see p. 6): "Some limited data support a potential waning of cases in warmer and more humid seasons, yet none are without major limitations...Additional studies as the SARS-CoV-2 pandemic unfolds could shed more light on the effects of climate on transmission."

With the above considerations in mind, our objective with this paper is to contribute to the knowledge basis regarding the spread of COVID-19 and the influence of environmental factors, particularly temperature, humidity, and sunshine. We adopt a population health approach, and report results from a spatial model of the incidence of COVID-19 in fifty provinces in Spain, one of the countries hardest hit by the pandemic. We combine data on reported cases of the disease with metereological information, to create a spatio-temporal dataset covering a period of 30 days. We then join this dataset with provincial-level economic and demographic information to act as controls to our key environmental variables. These data are analyzed using a spatial Seemingly Unrelated Regressions (SUR) approach, which allows us to model incidence of COVID-19 as a spatial contagion process.

The results provide evidence of the effect of temperature, humidity, and sunshine on the incidence of COVID-19. The clearest result with respect to these variables is a lower incidence of COVID-19 at higher temperatures and levels of humidity, while the opposite happens with respect to hours of sunshine. Our control variables also provide some intriguing insights. Higher incidence is associated with higher GDP per capita and presence of mass transit systems in the province; in contrast, population density and percentage of older adults display negative associations with incidence of COVID-19. The results of this analysis provide support to the hypothesis of seasonality of the novel SARS-CoV2, and should be of interest to public health officials and policy makers grappling with the question of the trajectory of the pandemic.

### 2020-04-18 README.Rmd
Updated the analysis to include hours of sunshine, revised the abstract and introduction to reflect this change, recreated the README.md document

Spreading with astonishing speed, the novel SARS-CoV2 has swept the globe, causing enormous stress to health systems and prompting social distance guidelines and mandates to arrest its progress. While there is encouraging evidence that early public health interventions have slowed the spread of the virus, this has come at a high cost as the global economy is brought to its knees. How and when to ease restrictions to movement hinges in part on the question whether SARS-CoV2 will display seasonality associated with variations in temperature and humidity. In this research, we address this question by means of a spatial analysis of the incidence of COVID-19 in the provinces in Spain. Use of a spatial Seemingly Unrelated Regressions (SUR) approach allows us to model the incidence of reported cases of the disease per 100,000 population, as a function of temperature and humidity, while controlling for GDP per capita, population density, percentage of older adults in the population, and presence of mass transit systems. An interesting aspect of the spatial SUR approach is that it models incidence as a contagion process. Our results indicate that incidence of the disease is lower at higher temperatures. The evidence with respect to humidity is more mixed, with coefficients for this variable that are significant in only some equations. Our control variables also yield interesting insights, as population density and percentage of older adults display negative associations with incidence of COVID-19, whereas the presence of mass transit systems in the province is associated with a greater incidence of the disease.

@@

SARS-CoV2  
COVID-19  
Seasonality  
Temperature  
Humidity  
Spatial SUR  
Contagion  
Spain

@@

<!--Equation for README.md generated using this app https://alexanderrodin.com/github-latex-markdown/-->

![\begin{equation} \label{eq:sur-sim} \begin{bmatrix} y_1 \\ y_2 \\ \vdots \\ y_T \end{bmatrix} = \begin{bmatrix} X_1 & 0 & \cdots & 0 \\ 0 & X_2 & \cdots & 0 \\ \vdots & \vdots & \ddots & \vdots \\ 0 & 0 & \cdots & X_T \end{bmatrix} \ \begin{bmatrix} \beta_1 \\ \beta_1 \\ \vdots \\ \beta_T \end{bmatrix} + \begin{bmatrix} \epsilon_1 \\ \epsilon_2 \\ \vdots \\ \epsilon_T \end{bmatrix} \end{equation}](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20%5Clabel%7Beq%3Asur-sim%7D%20%5Cbegin%7Bbmatrix%7D%20y_1%20%5C%5C%20y_2%20%5C%5C%20%5Cvdots%20%5C%5C%20y_T%20%5Cend%7Bbmatrix%7D%20%3D%20%5Cbegin%7Bbmatrix%7D%20X_1%20%26%200%20%26%20%5Ccdots%20%26%200%20%5C%5C%200%20%26%20X_2%20%26%20%5Ccdots%20%26%200%20%5C%5C%20%5Cvdots%20%26%20%5Cvdots%20%26%20%5Cddots%20%26%20%5Cvdots%20%5C%5C%200%20%26%200%20%26%20%5Ccdots%20%26%20X_T%20%5Cend%7Bbmatrix%7D%20%5C%20%5Cbegin%7Bbmatrix%7D%20%5Cbeta_1%20%5C%5C%20%5Cbeta_1%20%5C%5C%20%5Cvdots%20%5C%5C%20%5Cbeta_T%20%5Cend%7Bbmatrix%7D%20%2B%20%5Cbegin%7Bbmatrix%7D%20%5Cepsilon_1%20%5C%5C%20%5Cepsilon_2%20%5C%5C%20%5Cvdots%20%5C%5C%20%5Cepsilon_T%20%5Cend%7Bbmatrix%7D%20%5Cend%7Bequation%7D)

@@

\noindent where $A =I_{TN}-\bf{\Lambda} \otimes W$ with $\bf{\Lambda} = diag(\lambda_1, \cdots, \lambda_T)$.
-->

@@

<!--
This specification assumes that incidence in a province ($y_st$) at time $t$ is partially determined by the weighted average ($Wy_{st}$) of incidence in neighbouring provinces. Coefficients for the spatially lagged variable are estimated for each time period $\lambda_t$ and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence ($\lambda_i=\lambda_j, \forall i,j$). The correspond Wald test is available in the `R` package `spsur`.
-->

@@

Summary of best model.
```{r summary-best-model, echo=FALSE, cache = TRUE}
data.frame(Coefficient = sur.slm_lag11$coefficients, 
           pval = dnorm(abs(sur.slm_lag11$coefficients/sur.slm_lag11$rest.se))) %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Variable = c("Intercept", 
                      "log(GDPpc)", 
                      "log(Older)",
                      "log(Density)",
                      "Transit",
                      "log(Humidity)",
                      "log(Temperature)",
                      rep(c("Intercept",
                            "log(Density)", 
                            "Transit", 
                            "log(Humidity)", 
                            "log(Temperature)"), 29)),
         Variable = factor(Variable, 
                           levels = c("Intercept", 
                                      "log(GDPpc)", 
                                      "log(Older)", 
                                      "log(Density)",
                                      "Transit", 
                                      "log(Humidity)",
                                      "log(Temperature)"))) %>%
  group_by(Variable) %>%
  summarize(Min = min(Coefficient), 
            Mean = mean(Coefficient), 
            Max = max(Coefficient),
            pns = sum(pval > 0.10), # Number of coefficients with p > 0.1
            p10 = sum(pval <= 0.10) - sum(pval <= 0.05), # Number of coefficients with  0.1 <= pval < 0.05
            p05 = sum(pval <= 0.05)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Non-constrained", 
                  "Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained")) %>%
  kable(#"latex",
        "html",
        booktabs = TRUE,
        digits = 3,
        col.names = c("Variable", "Min", "Mean", "Max", "p > 0.10", "0.10 <= p < 0.05", "p <= 0.05", "Note"),
        caption = "\\label{tab:summary-best-model}Summary of estimation results best model (lagged 11-day moving average)") %>%
  #kable_styling(latex_options = c("striped", "scale_down")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  add_header_above(c(" " = 1, "Estimates" = 3, "Significance" = 3, " " = 1)) %>%
  footnote(general = c("Significance: This is the number of coefficients with p-values as indicated",
                       "Non-constrained: coefficient was allowed to vary across equations",
                       "Constrained: coefficient as constant across equations"))
```

>>>>

  Spreading with astonishing speed, the novel SARS-CoV2 has swept the globe, causing enormous stress to health systems and prompting social distance guidelines and mandates to arrest its progress. While there is encouraging evidence that early public health interventions have slowed the spread of the virus, this has come at a high cost as the global economy is brought to its knees. How and when to ease restrictions to movement hinges in part on the question whether SARS-CoV2 will display seasonality associated with variations in temperature, humidity, and hours of sunshine. In this research, we address this question by means of a spatial analysis of the incidence of COVID-19 in the provinces in Spain. Use of a spatial Seemingly Unrelated Regressions (SUR) approach allows us to model the incidence of reported cases of the disease per 100,000 population, as a function of temperature and humidity, while controlling for GDP per capita, population density, percentage of older adults in the population, and presence of mass transit systems. An interesting aspect of the spatial SUR approach is that it models incidence as a contagion process. Our results indicate that incidence of the disease is lower at higher temperatures and higher levels of humidity, although coefficients for this variable are significant only in some equations. Sunshine, in contrast, displays a positive association with incidence of the disease. Our control variables also yield interesting insights. Higher incidence is associated with higher GDP per capita and presence of mass transit systems in the province; in contrast, population density and percentage of older adults display negative associations with incidence of COVID-19.

@@

SARS-CoV2  
COVID-19  
Seasonality  
Temperature  
Humidity  
Population density  
Older adults  
Spatial SUR  
Contagion  
Spain

@@

<!--Equation for README.md generated using this app https://alexanderrodin.com/github-latex-markdown/-->
![\begin{equation} \label{eq:sur-sim} \begin{bmatrix} y_1 \\ y_2 \\ \vdots \\ y_T \end{bmatrix} = \begin{bmatrix} X_1 & 0 & \cdots & 0 \\ 0 & X_2 & \cdots & 0 \\ \vdots & \vdots & \ddots & \vdots \\ 0 & 0 & \cdots & X_T \end{bmatrix} \ \begin{bmatrix} \beta_1 \\ \beta_1 \\ \vdots \\ \beta_T \end{bmatrix} + \begin{bmatrix} \epsilon_1 \\ \epsilon_2 \\ \vdots \\ \epsilon_T \end{bmatrix} \end{equation}](https://render.githubusercontent.com/render/math?math=%5Cbegin%7Bequation%7D%20%5Clabel%7Beq%3Asur-sim%7D%20%5Cbegin%7Bbmatrix%7D%20y_1%20%5C%5C%20y_2%20%5C%5C%20%5Cvdots%20%5C%5C%20y_T%20%5Cend%7Bbmatrix%7D%20%3D%20%5Cbegin%7Bbmatrix%7D%20X_1%20%26%200%20%26%20%5Ccdots%20%26%200%20%5C%5C%200%20%26%20X_2%20%26%20%5Ccdots%20%26%200%20%5C%5C%20%5Cvdots%20%26%20%5Cvdots%20%26%20%5Cddots%20%26%20%5Cvdots%20%5C%5C%200%20%26%200%20%26%20%5Ccdots%20%26%20X_T%20%5Cend%7Bbmatrix%7D%20%5C%20%5Cbegin%7Bbmatrix%7D%20%5Cbeta_1%20%5C%5C%20%5Cbeta_1%20%5C%5C%20%5Cvdots%20%5C%5C%20%5Cbeta_T%20%5Cend%7Bbmatrix%7D%20%2B%20%5Cbegin%7Bbmatrix%7D%20%5Cepsilon_1%20%5C%5C%20%5Cepsilon_2%20%5C%5C%20%5Cvdots%20%5C%5C%20%5Cepsilon_T%20%5Cend%7Bbmatrix%7D%20%5Cend%7Bequation%7D)

@@

\noindent where $A =I_{TN}-\bf{\Lambda} \otimes W$ with $\bf{\Lambda} = diag(\lambda_1, \cdots, \lambda_T)$.

This specification assumes that incidence in a province ($y_st$) at time $t$ is partially determined by the weighted average ($Wy_{st}$) of incidence in neighbouring provinces. Coefficients for the spatially lagged variable are estimated for each time period $\lambda_t$ and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence ($\lambda_i=\lambda_j, \forall i,j$). The correspond Wald test is available in the `R` package `spsur`. 
-->

@@

@@

Summary of best model.
```{r summary-best-model, echo=FALSE, cache = TRUE}
data.frame(Coefficient = sur.slm_lag11$coefficients, 
           pval = dnorm(abs(sur.slm_lag11$coefficients/sur.slm_lag11$rest.se))) %>%
  rownames_to_column(var = "Variable") %>%
  mutate(Variable = c("Intercept", 
                      "log(GDPpc)", 
                      "log(Older)",
                      "log(Density)",
                      "Transit",
                      "log(Humidity)",
                      "log(Temperature)",
                      "log(Sunshine)",
                      rep(c("Intercept",
                            "log(Density)", 
                            "Transit", 
                            "log(Humidity)", 
                            "log(Temperature)",
                            "log(Sunshine)"),
                          29)),
         Variable = factor(Variable, 
                           levels = c("Intercept", 
                                      "log(GDPpc)", 
                                      "log(Older)", 
                                      "log(Density)",
                                      "Transit", 
                                      "log(Humidity)",
                                      "log(Temperature)",
                                      "log(Sunshine)"))) %>%
  group_by(Variable) %>%
  summarize(Min = min(Coefficient), 
            Mean = mean(Coefficient), 
            Max = max(Coefficient),
            pns = sum(pval > 0.10), # Number of coefficients with p > 0.1
            p10 = sum(pval <= 0.10) - sum(pval <= 0.05), # Number of coefficients with  0.1 <= pval < 0.05
            p05 = sum(pval <= 0.05)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Non-constrained", 
                  "Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained")) %>%
  kable(#"latex",
        "html",
        booktabs = TRUE,
        digits = 3,
        col.names = c("Variable", "Min", "Mean", "Max", "p > 0.10", "0.10 <= p < 0.05", "p <= 0.05", "Note"),
        caption = "\\label{tab:summary-best-model}Summary of estimation results best model (lagged 11-day moving average)") %>%
  #kable_styling(latex_options = c("striped", "scale_down")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  add_header_above(c(" " = 1, "Estimates" = 3, "Significance" = 3, " " = 1)) %>%
  footnote(general = c("Significance: This is the number of coefficients with p-values as indicated",
                       "Non-constrained: coefficient was allowed to vary across equations",
                       "Constrained: coefficient as constant across equations"))
```
